### 2016-06-23 manuscript/supplementary.tex
Increased the number of permutations. Reordered R code.

>>>>

\section*{R code for Figure~1A\&B}

{\tiny
\begin{verbatim}

#read data
d <-read.table("meanRankSpeedData.tsv", header=T)

#initialize matrices
dNames <- c("IF", "H5", "relAge",       "yearPublished", "cites", "relCites",       "mindex",  "hindex",  "accuracyRank",  "speedRank" )
pNames <- c("JIF", "JH5", "Rel. age", "Year",          "Cites", "Rel. cites", "M-index", "H-index", "Accuracy",      "Speed")
pvalMatrix<-matrix(1, length(dNames), length(dNames))
rhoMatrix <-matrix(0, length(dNames), length(dNames))
sigMatrix <-matrix("",length(dNames), length(dNames))

colnames(pvalMatrix)<-pNames
rownames(pvalMatrix)<-pNames
colnames(rhoMatrix) <-pNames
rownames(rhoMatrix) <-pNames
colnames(sigMatrix) <-pNames
rownames(sigMatrix) <-pNames

#loop through pairwise combinations, record rho and P-values 
for(i in 1:length(dNames)){
      for(j in 1:length(dNames)){
	    spear<-cor.test(d[,dNames[i] == colnames(d)], d[,dNames[j] == colnames(d)], method = "spearman", exact = T)   #, alternative = "less")
	    pvalMatrix[i,j] <- spear$p.value 
	    rhoMatrix[i,j]  <- spear$estimate
	    if(spear$p.value < 0.05){
		sigMatrix[i,j]  <- "X"
	    }
      }
}

#generate plots
pdf(file=    "../figures/spearmanHeatmap.pdf", width = 7,  height = 6)
par(mar = c(8,4,4,4) + .1) #c(bottom, left, top, right). default: c(5, 4, 4, 2) + 0.1
heatmap.2(rhoMatrix, cellnote=sigMatrix,notecex=1.5,notecol="black", col=redblue(40), density.info="none", trace="none", dendrogram=c("column"), symm=F,symkey=T,symbreaks=T,
	scale="none", key.title = "", srtRow=45, adjRow=c(0, 1), srtCol=45, adjCol=c(1,1), breaks=(-20:20)/20,
margins = c(8, 8), cexRow=1.5, cexCol=1.5)
dev.off()

relCitesA<-cor.test(1-d$accuracyRank, as.numeric(d$relCites),     method = "spearman")
hindexA  <-cor.test(1-d$accuracyRank, as.numeric(d$hindex),       method = "spearman")
mindexA  <-cor.test(1-d$accuracyRank, as.numeric(d$mindex),       method = "spearman")
H5A      <-cor.test(1-d$accuracyRank, as.numeric(d$H5),           method = "spearman")
relAgeA  <-cor.test(1-d$accuracyRank, as.numeric(d$relAge),       method = "spearman")
speedA   <-cor.test(1-d$accuracyRank, as.numeric(d$speedRank),    method = "spearman")
citesA   <-cor.test(1-d$accuracyRank, as.numeric(d$cites),        method = "spearman")
IFA      <-cor.test(1-d$accuracyRank, as.numeric(d$IF),           method = "spearman")
yearA    <-cor.test(1-d$accuracyRank, as.numeric(d$yearPublished),method = "spearman")

pdf(file=    "../figures/spearmanBarplot.pdf", width = 5,  height = 3)
op<-par(mfrow=c(1,1),cex=1.0,las=2)
barplot(t(c(mindexA$estimate, hindexA$estimate, relAgeA$estimate, H5A$estimate, speedA$estimate, citesA$estimate, relCitesA$estimate, yearA$estimate, IFA$estimate)),
	names=c("M-index", "H-index", "Rel. age", 'JH5', "Speed", "Cites", "Rel. cites", "Year", "JIF"), ylab="Spearman's rho",ylim=c(-0.1,0.1),main="Correlates with accuracy rank")
lines(c(-100,100),c(0,0))
dev.off()
\end{verbatim}
}
